Geometric variational problems

### 2020-11-13 NSF2020/Description/preliminarywork.tex
RJR getting there one prelim work

\section{Preliminary work}
\label{sec:preliminary_work}
\subsection{Estimating two-dimensional elastic moduli} The motivation
for Specific Aims 1-3 stemmed from the successful demonstration of
gradient driven self-assembly of amphiphilic particles into
two-dimensional micelles, bilayer membranes~\cite{Fu2018_SIAM}, and
recreation of the vesicles tank-treading phenomenon.

Our preliminary work on membrane elasticity is particulary encouraging
because the effective bending, stretch, and tilt elastic moduli we
calculated were in excellent agreement with the experimental values
(Table~\ref{tab:moduli}).  The agreement is underscored by the fact we
assigned reasonable physical values to the main model parameters of HAP
energy, rather than tuning parameters.

\begin{table}[h!]
\begin{center}
  \begin{tabular}{|l|p{0.16\textwidth}|l|l|p{0.2\textwidth}|p{0.18\textwidth}}
    \hline
          & simulation type & HAP value        & experimental value & reference\\
    \hline \hline 
    $\KB$ & {\footnotesize uniform load with clamped condition} & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & {\footnotesize bilayer stretching}  & $34$ \kBT $^{-2}$ & 30--40 \kBT $^{-2}$              & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & {\footnotesize tilt Dirichlet condition} & $12$ \kBT \; nm$^{-2}$ & 10 \kBT $^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
\end{center}
\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
  moduli from the experimental literature and values derived by HAP
  simulation.} 
\end{table}

>>>>

\section{Preliminary work}
\label{sec:preliminary_work}
The HAP project was initiated in 2017 by PIs RR and YNY.
The lead author on our first paper (\cite{Fu2018_SIAM}) was Szu-Pei Fu,
who was PI YNS's PhD student and is currently a postdoc with PI RR.
The collaboration involved theoretical work and simulation. The theoretical
work included model development, proving the first variation formula
\eqref{stress} and force-free law, and an energy-based  uniqueness
theorem for the exterior domain problem \eqref{SL}.
Coauthors Andreas Kl\"ockner (Computer Science, UIUC, NSF CAREER \#1654756)
and his PhD student Matt Wala provided their Quadrature by Expansion, or QBX
algorithm and Fu ran simulations on NJIT clusters.

The simulation results were encouraging. The small particle-number
simulations successfully demonstrated gradient-driven self-assembly of amphiphilic
particles into two-dimensional micelles, bilayer membranes. The model parameters
where the decay length $\rho$, interfacial tension $\gamma$, particle geometry, and
repulsion strength. The particle diamaters were set equal to monolayer thickness, 2.0 nm \cite{Boal}, and we chose a repulsion strength that gave adequate interparticle spacing.
For the decay length, we used $\rho = 2.5$ nm based on measurements of hydrophobic
attraction between surfactant-coated \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80}.
For the interfacial tension, we used $\gamma = 4$ pN nm$^{-1}$
based on measurements for single-component bilayer lipid membranes
\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.

\begin{wraptable}[10]{r}{0.55\textwidth}
\begin{center}
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP         & exper. value & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$  & $34$ \kBT nm$^{-2}$ & 30--40 \kBT nm$^{-2}$              & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$  & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
\end{center}
\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
  moduli from the experimental literature and values derived by HAP
  simulation.} 
\end{wraptable}
We performed three types of simulations. The first measured bending by loading
a planar bilayer. The second used a harmonic bond to dilate a circular bilayer.
The third measured tilt using a decay equation from  \cite{KUZMIN2005}.
These simulations isolated the deformations of \eqref{ansatz3}, enabling
us to read off elastic moduli from simulation data. 
The results agreed remarkably well with the values reported in the experimental literature, 
Table~\ref{tab:moduli}. The agreement is underscored by the fact
that the two, main HAP parameters $\gamma$ and $\rho$ were assigned
physical values from the outset, rather than being tuned.
